---
title: "Timothy Gan, Randal Donaldson"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data(mpg)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r ABIA, message=TRUE, warning=TRUE}
library(tidyverse)
ABIA = read.csv("data/ABIA.csv")
security_summ = ABIA %>%
  group_by(DayOfWeek)  %>%  # group the data points by model name
  summarize(DepartureDelay.mean = mean(DepDelay, na.rm=TRUE))  # calculate a mean for each model

ggplot(security_summ, aes(x=DayOfWeek, y=DepartureDelay.mean)) + 
  geom_bar(stat='identity')
```
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
