---
title: "Timothy Gan, Randal Donaldson"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)
ABIA = read.csv("data/ABIA.csv")
creatinine = read.csv("data/creatinine.csv")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## ABIA

Look at these departure delays!

```{r ABIA, message=TRUE, warning=TRUE, echo=FALSE}

security_summ = ABIA %>%
  group_by(DayOfWeek)  %>%  # group the data points by model name
  summarize(DepartureDelay.mean = mean(DepDelay, na.rm=TRUE))  # calculate a mean for each model

ggplot(security_summ, aes(x=DayOfWeek, y=DepartureDelay.mean)) + 
  geom_bar(stat='identity')
```
```

## Creatinine

muscle poop:

```{r creatinine, echo=FALSE}
plot(creatclear ~ age, data = creatinine)

lm1 = lm(creatclear ~ age, data = creatinine)
abline(147.81, -0.619)


```

